Title here

### 2017-01-03 portfolio/text/ms.Rmd
Slash abstract

<!-- Diversified portfolios of fishing permits and species reduce risk for fishermen, -->
<!-- but changing species diversity can be risky, costly, and limited by regulations. -->
<!-- Goal: Introduction, Methods, Results, Discussion, Conclusion:
<!-- 600, 900, 500, 800, 200, -->

@@

<!-- TODO slash length of abstract -->

A fundamental challenge for individuals who rely on the extraction of natural
resources for their livelihood is income variability. Fishers, loggers, farmers,
and miners, among others, face high levels of income uncertainty driven by a mix
of environmental, biological, and economic variability. A key component
underlying the sustainability of these industries is identifying both how
regulatory actions and individual behaviour affect income variability and by
extension the economic stability and sustainable use of natural resources. For
commercial fisheries, recent work has identified that targeting a diversity of
species can reduce income variability. However, any diversity-variability
relationship is embedded in a regulatory framework that restricts individual
ability to change fishing behaviour. Here we identify three primary axes by
which fishers in Alaska, one of the world's most productive fishery regions, can
potentially diversify fishing activities and investigate how individual actions
along each diversity axis affect both revenue and revenue variability. We
construct a novel statistical model to simultaneously assess the value to
individual fishers of choosing to (1) own permits that allow targeting a diverse
fish species assemblage, (2) diversify by owning multiple permits, or (3) catch
a greater species diversity within the constraints of a given permit. We show
contrasting effects of diversity on revenue and revenue variability along the
three axes. First, we show that fishing permits with higher species diversity
reduces variability (`r h1[[2]]`% [`r h1[[1]]`--`r h1[[3]]`% 95% CI] reduction
per unit increase in mean effective species diversity). Next, we show that
fishing an additional permit is associated with higher revenue and lower
variability (e.g., `r 100-spoke[[2]]`% [`r 100-spoke[[3]]`--`r 100-spoke[[1]]`%
IQR] decline in standard deviation for fishers with halibut and another permit
vs. only a halibut permit). Finally, we show that increasing species diversity
within the constraints of a permit set has a fishery-dependent effect on revenue
and is usually (`r g2_dens`% probability) associated with increased uncertainty
in revenue the following year. Thus, while there are clear benefits to some axes
of diversification, others are less effective. Importantly, the most effective
mechanism for increasing revenue and decreasing risk --- purchasing additional
permits to participate in additional fisheries --- was also the most costly.
Furthermore, the least costly option of increasing catch diversity within an
existing permit was associated with increased revenue variability. Thus, over
the past 30 years as the Alaskan commercial fishing fleet has become
increasingly specialized and most individuals only participate under a single
permit, the practical benefits accrued from increased species diversification
are limited.

Our results suggest that the benefit of species diversity for revenue
variability is mostly an across-permit effect, not a benefit that can be easily
harnessed by an individual permit holder. Effective methods of diversification
--- purchasing additional permits or switching permits --- are costly and often
limited by regulations such as limited entry programs and individual
transferable quotas (ITQs). Take home ...

>>>>

<!-- Introduction, Methods, Results, Discussion, Conclusion -->
<!-- 600, 900, 500, 800, 200, -->

@@

<!-- TODO < 250 words -->

Individuals who rely on the extraction of natural resources for their
livelihood --- fishers, farmers, and loggers, among others --- face high levels
of income variability driven by a mix of environmental, biological, and
economic variability.
A key component to managing these industries is identifying how regulatory
actions and individual behaviour affect income variability and by extension the
economic stability and sustainable use of natural resources. For commercial
fisheries, recent work has identified that communities and vessels can lower
revenue variability by increasing the diversity of species fished. 
<!-- fix: One sentence clearly stating the general problem being addressed by
this particular study --> 
However, it is unclear if ... extend to individual... year to year changes
<!-- cut down, 1 sentence: -->
Here we identify three axes by which fishers in Alaska, one of the world's most
productive fishery regions, can potentially diversify fishing activities and
investigate how individual actions along each diversity axis affect revenue and
revenue variability. 
<!-- We simultaneously assess the value to individual fishers of choosing to (1) own -->
<!-- permits that allow targeting a diverse fish species assemblage, (2) diversify -->
<!-- by adding additional permits, or (3) catch a greater species diversity within -->
<!-- the constraints of a given permit. --> 
We show that fishing permits with higher species diversity reduces revenue
variability and fishing an additional permit is associated with higher revenue
and lower variability. However, increasing species diversity within the
constraints of a permit set has a fishery-dependent effect on revenue and is
usually (`r g2_dens`% probability) associated with increased uncertainty in
revenue the following year. 
Our results suggest that the benefit of species diversity for reducing revenue
variability is mostly an across-permit effect, not a benefit that can be easily
harnessed by individual permit holders. The most effective mechanism for
increasing revenue and decreasing variability --- purchasing permits to
participate in additional fisheries --- is also the most costly and often
limited by regulations such as limited entry and catch share programs.

<!-- Thus, over the past 30 years as the Alaskan commercial fishing fleet has become -->
<!-- increasingly specialized, -->
